\section{The interval-Krawczyk certification method}
\label{sec:certification}

\TODO{Full prose drawn from \path{docs/preprint_outline.md} Section~3
and \path{THEOREM.md} provenance section. Implementation pointers:
\path{scripts/witness.py}, \path{scripts/exact.py},
\path{scripts/interval.py}, \path{scripts/certificate.py},
\path{scripts/sweep.py}, \path{scripts/verify_sweep.py}.}

\subsection{Numerical witness search}
\label{sec:certification-witness}

\TODO{Levenberg--Marquardt on the Kirchhoff~+~unit-norm system with
multi-seed retry. Discuss the two failure modes (saddle plateau and
near-singular Jacobian) and the seed-rotation remedy.}

\subsection{Gauge fix and Newton refinement}
\label{sec:certification-refine}

\TODO{Pin vertex 0's spokes; Newton refinement to 50 decimal digits
in \texttt{mpmath} over $\Q[s]/(s^{2}-3)$ to keep $\sqrt 3$ exact.
Drop one redundant vertex to get a square system
(\cref{lem:square-system}).}

\subsection{Interval Krawczyk}
\label{sec:certification-krawczyk}

\TODO{State the Krawczyk theorem and the operator
\[
   K(\mathbf{I}) \;=\; c - Y\,F(c) + (E - Y\,J(\mathbf{I}))(\mathbf{I} - c),
   \qquad Y = J(c)^{-1},
\]
with $\mathbf{I} = [c - 10^{-5},\, c + 10^{-5}]$ componentwise.
Containment $K(\mathbf{I}) \subset \mathrm{int}(\mathbf{I})$ implies a
unique zero of $F$ in $\mathbf{I}$.}

\paragraph{Numerical gotchas.}
\TODO{Two implementation points worth flagging: (i) the centre term
$F(c)$ must be evaluated at a \emph{point}, not on the interval box,
otherwise the Krawczyk margin grows linearly in the box radius;
(ii) \texttt{sympy.lambdify} with \texttt{modules=None} keeps
half-integer coefficients as Python floats (exact for halves), while
\texttt{modules='mpmath'} introduces \texttt{mpf}/\texttt{iv.mpf}
conversion errors. See \path{scripts/interval.py} for the exact form.}

\subsection{Schema-v2 replayable certificate}
\label{sec:certification-replay}

\TODO{JSON document containing: graph6, canonical edge order, pinning
data, dropped redundant vertex index, free-variable list,
polynomial-system SHA-256, decimal-string centre, per-coordinate
Krawczyk margins, full provenance metadata
(Python/mpmath/sympy/networkx versions, OS, hostname). Replayer
reconstructs the polynomial system, verifies the hash, re-evaluates
the Krawczyk operator, and emits a verdict. See
\path{docs/external_replay} for the cold-environment log.}
