\section{The constructive closure theorem}
\label{sec:gadget-closure}

\TODO{Prose from \path{docs/preprint_outline.md} Section~6 and
\path{docs/gadget_closure.md}. Statement of \cref{thm:B-intro} in its
formal form together with the two closed-form gadget flow extensions.}

\subsection{Triangle blow-up}
\label{sec:gadget-triangle}

\TODO{Definition: replace a degree-3 vertex $v$ with three new
vertices $v_1, v_2, v_3$ forming a triangle, each $v_i$ inheriting
one of $v$'s spokes. Closed-form $\Sphere$-flow extension on the
triangle:
\[
   g_{12} = \frac{f_2 - f_1}{3} + \varepsilon \sqrt{\tfrac{2}{3}}\,\hat n,
   \quad g_{13} = -f_1 - g_{12}, \quad g_{23} = -f_2 + g_{12},
\]
with $\hat n = (f_3 \times (f_2 - f_1))/\Vert\cdot\Vert$ and
chirality $\varepsilon \in \{\pm 1\}$. Verification via
\path{scripts/triangle_blowup.py} at residual $\le 1.7\cdot 10^{-16}$.}

\begin{lemma}[Triangle blow-up preserves $\Sphere$-flow existence]
\label{lem:triangle-blowup}
\TODO{Formal statement and short proof from the closed form above.}
\end{lemma}

\subsection{Three-edge-cut dot product}
\label{sec:gadget-dot}

\TODO{Definition: $G_1 \oplus_\pi G_2$ glues at vertices $v_1, v_2$
by three through-edges with permutation $\pi$. Flow consistency
forces the boundary triple of $G_2$ to equal $-T_1 \circ \pi$ after
some $R \in \SO(3)$. \texttt{align\_to\_negation} Kabsch-searches the
six permutations; succeeds when the chiralities match.}

\begin{lemma}[Dot product preserves $\Sphere$-flow existence]
\label{lem:dot-product}
\TODO{Statement and short proof from the Kabsch construction.}
\end{lemma}

\subsection{The closure theorem}
\label{sec:gadget-theorem}

\begin{theorem}[Constructive closure, formal version]
\label{thm:B}
\TODO{Formal restatement of \cref{thm:B-intro}, with the closed-form
flow extension. The proof is by induction on the operation tree using
\cref{lem:triangle-blowup,lem:dot-product}.}
\end{theorem}

\paragraph{Verified instances.}
\TODO{Table: triangle blow-up on Petersen, Blanu\v{s}a-1, $J_5$; dot
products P$\oplus$P, P$\oplus$B$_1$, $J_5 \oplus J_5$; iterated chains
$P^{\oplus 4}$ and $P \oplus J_5 \oplus B_1$. Each with the maximum
Kirchhoff residual at machine precision.}

\subsection{Relation to the snark world}
\label{sec:gadget-not-snarks}

\TODO{Note that $\closure \not\subseteq$ snarks: triangle blow-up
shatters girth $\ge 5$, dot product shatters cyclic 4-edge-connectivity.
$\closure$ is, however, strictly larger than $\base$ as a class of
cubic graphs with constructive $\Sphere$-flows, and the construction
is \emph{parametric} in the gadget sequence (no per-graph Krawczyk
needed beyond the 3247 base certificates).}
