\section{The decomposition frontier and replayable membership}
\label{sec:decomposition-frontier}

\TODO{Prose from \path{docs/preprint_outline.md} Section~7 and
\path{docs/gadget_decomposition_frontier.md}. Formal statement of
\cref{thm:C-intro} and the dynamic programming decision procedure.}

\subsection{Inverse operations}
\label{sec:decomposition-inverses}

\TODO{Definitions of inverse triangle reduction and inverse 3-edge-cut
dot product. Correctness lemmas that each is the left inverse of the
corresponding forward operation up to isomorphism.}

\begin{lemma}[Inverse triangle reduction]
\label{lem:inverse-triangle}
\TODO{A triangle $\{u_1, u_2, u_3\}$ in a cubic graph $G$ is
\emph{contractible} iff each $u_i$ has exactly one external neighbour
$e_i$ and $e_1, e_2, e_3$ are pairwise distinct. The contraction
yields a simple cubic graph with $|V(G)| - 2$ vertices, isomorphic to
the unique cubic graph $G'$ such that the triangle blow-up of $G'$ at
some vertex is $G$.}
\end{lemma}

\begin{lemma}[Inverse 3-edge-cut dot product]
\label{lem:inverse-dot}
\TODO{A cyclic $3$-edge cut $C$ in a cubic graph $G$ splits $G$ into
two pieces, each containing a cycle; adding a fresh vertex on each
side connected to the three cut-edge endpoints recovers the unique
ordered pair of cubic graphs whose dot product (along $C$) is $G$ up
to isomorphism.}
\end{lemma}

\subsection{Isomorphism via canonical \texttt{graph6}}
\label{sec:decomposition-canonical}

\TODO{Use \texttt{labelg} from \texttt{nauty}~\cite{nauty} to compute
the canonical \texttt{graph6} string of each candidate piece. Two
graphs are isomorphic iff their canonical strings are equal. The DP
memoises by canonical string.}

\subsection{The decomposition theorem}
\label{sec:decomposition-theorem}

\begin{theorem}[Decomposition frontier, formal version]
\label{thm:C}
\TODO{Formal restatement of \cref{thm:C-intro}. Proof:
\begin{enumerate}[label=(\arabic*)]
  \item Every $G \in \base$ has girth $\ge 5$ (no triangles) and is
        cyclically $\ge 4$-edge-connected (no cyclic 3-cuts); thus
        $G$ is irreducible under both inverse operations.
        Empirically verified by exhaustive scan over all 3247
        catalogue graphs.
  \item The DP procedure \texttt{decompose\_tree}$(G, \base)$
        terminates because every inverse operation strictly decreases
        the vertex count; correctness follows from the
        \cref{lem:inverse-triangle,lem:inverse-dot} round-trip
        properties.
\end{enumerate}}
\end{theorem}

\subsection{Replayable membership certificates}
\label{sec:decomposition-replay}

\TODO{Format: a \texttt{DecompTree} with operation labels at each
internal node and base-graph6 strings at the leaves. To verify $G \in
\closure$ a third party: (i) reconstructs $G$ from its graph6; (ii)
follows the tree, performing the indicated inverse operations,
canonicalising each intermediate; (iii) checks that each leaf's
graph6 matches a certified base entry; (iv) reads off the constructive
$\Sphere$-flow by composing the gadget extensions from the leaves up.}

\paragraph{Verified positive examples.}
\TODO{Table: blow-up of Petersen (depth 1), double blow-up (depth 2),
$P \oplus P$ (depth 1), $P \oplus P \oplus B_1$ (depth 2), blow-up of
triple chain (depth 3). All decompositions verified by replay.}
