\section{Reproducibility}
\label{sec:reproducibility}

\TODO{Prose from \path{docs/preprint_outline.md} Section~9. The whole
package replays bit-for-bit from the committed certificate files.}

\subsection{Hardware and software stack}
\label{sec:repro-stack}

\TODO{Reference machine specification (single laptop class, CPU
model). Software: Python~3.12, mpmath~1.3, sympy~1.13, networkx~3.6,
scipy~1.14, nauty~2.9.3, snarkhunter~2.0b, python-sat~1.8.}

\subsection{Build and run}
\label{sec:repro-build}

\TODO{Instructions:
\begin{itemize}
  \item Clone the repository.
  \item Create a uv virtual environment: \texttt{uv venv}, then
        \texttt{uv pip install -r requirements.txt}.
  \item Build nauty and snarkhunter from the included source archives.
  \item \texttt{make verify}: full \texttt{pytest} suite ($\sim 2$~min).
  \item \texttt{make verify-certs}: replay all 3247 interval-Krawczyk
        certificates ($\sim 30$~min single-thread).
  \item \texttt{make catalogue}: regenerate the catalogue from scratch
        ($\sim 30$~min through $n = 26$; $\sim 25$~min for $n = 28$
        via snarkhunter).
  \item \texttt{make manifest}: verify catalogue SHA-256 against the
        committed manifest.
\end{itemize}
}

\subsection{File-level provenance}
\label{sec:repro-provenance}

\TODO{Schema-v2 certificate format documented in
\cref{sec:certification-replay}. Graph6 canonicalisation contract:
\texttt{nauty} \texttt{labelg} is the canonical form; commits include
the version pin. Cold-environment replay log at
\path{docs/external_replay} records the $3247/3247$ re-verification
on an unrelated machine with no shared code with the original
certifier.}

\subsection{What is and is not committed}
\label{sec:repro-commits}

\TODO{The Krawczyk certificates and the catalogue graph6 streams are
committed. The raw geng/snarkhunter output is not committed (gigabytes
of intermediate data); the reproducibility instructions tell a third
party how to regenerate it. The numerical witnesses are committed
inside the certificates (decimal-string form, full precision).}
